ASLO 2021

### 2022-12-20 scripts/ASLO_2021_2.Rmd

```{r results='hide', message=FALSE, warning=FALSE}
# load libraries
library(sf) # spatial data
library(gstat) # lagged scatterplot, variogram
library(tidyverse) # dplyr, ggplot
library(janitor) # clean names
library(spdep) # k-NN and Moran plot
library(ncf) # ncf::correlogram
library(lattice) # xyplot
library(micromap) # linked micromaps

@@

## Site Map
```{r}
# Load data
 load(paste0(localPath,
            "/Environmental Protection Agency (EPA)/",
            "ORD NLA17 Dissolved Gas - Documents/",
            "inputData/dg.2021-02-01.RData"))

@@

## Population Data
Roy Martin predicted dissolved N2O concentration (preds_n2O), dissolved equilibrium N2O concentration (preds_n2oeq), and N2O saturation ratio (preds_sat) for all waterbodies in the population.  See his .rmd for more details.  
```{r}
# about 15 minutes to load first time
# 6/7/21 <2 minutes
Sys.time()
load(paste0(localPath, "\\Environmental Protection Agency (EPA)\\ORD NLA17 Dissolved Gas - Documents\\inputData\\all_predictions.rda"))
Sys.time()
```

@@

# point and linerange
all_predictions %>%
  group_by(WSA9, .draw) %>%
  #group_by(.draw) %>%
  summarise( mean_sat = mean(preds_sat)) %>%
  summarise( estimate = round(median(mean_sat), 3),
    LCL = round(quantile(mean_sat, probs = 0.025), 3),
    UCL = round(quantile(mean_sat, probs = 0.975), 3)) %>% 
  mutate(ecoregion = factor(WSA9)) %>%
  #mutate(type = "MR") %>%
  select(ecoregion, estimate, LCL, UCL) %>%
  mutate(ecoregion = fct_reorder(ecoregion, estimate)) %>%
  ggplot( aes( x = ecoregion, y = estimate ) ) +
  geom_point() +
  geom_linerange( aes( ymin = LCL, ymax = UCL)) +
  geom_hline(yintercept = 1, color='blue') +
  ylab("mean N2O saturation ratio") +
  coord_flip() + 
  theme_bw() +
  ggtitle("Mean (+/- 95% CI) predicted N2O saturation ratio")

# density plots of predicted distribution
# huge right tail
p <- all_predictions %>%
  filter(.draw %in% 1:10) %>% # subset for practice
  mutate(ecoregion = factor(WSA9)) %>%
  mutate(ecoregion = fct_reorder(ecoregion, preds_sat)) %>%
  ggplot( aes( x = preds_sat, group = .draw, color = .draw ) ) +
  geom_density(show.legend = FALSE) +
  geom_vline(xintercept = 1, color = "red") +
  xlab("N2O saturation ratio") +
  xlim(0,5) + # data range is 0-600, but sample max is 30
  facet_wrap(~ecoregion) +
  theme_bw()

>>>>

```{r results='hide', message=FALSE, warning=FALSE}
# load libraries
library(sf) # spatial data
library(gstat) # lagged scatterplot, variogram
library(tidyverse) # dplyr, ggplot
library(janitor) # clean names
library(spdep) # k-NN and Moran plot
library(ncf) # ncf::correlogram
library(lattice) # xyplot
library(micromap) # linked micromaps
library(tictoc) # time operations

@@

## Site Map
```{r}
# Load data.  Loaded object is named dg.
 load(paste0(localPath,
            "/Environmental Protection Agency (EPA)/",
            "ORD NLA17 Dissolved Gas - Documents/",
            "inputData/dg.2021-02-01.RData"))

@@

## Population Data
Roy Martin predicted dissolved N2O concentration (preds_n2O), dissolved equilibrium N2O concentration (preds_n2oeq), and N2O saturation ratio (preds_sat) for all waterbodies in the population.  See his .rmd for more details.  
```{r}
# 12/14/22 <2 minutes
tic()
load(paste0(localPath, "\\Environmental Protection Agency (EPA)\\ORD NLA17 Dissolved Gas - Documents\\inputData\\all_predictions.rda"))
toc()
```

@@

# point and linerange
all_predictions %>%
  group_by(WSA9, .draw) %>%
  #group_by(.draw) %>%
  summarise(mean_sat = mean(n2osat)) %>%
  summarise(estimate = round(median(mean_sat), 3),
    LCL = round(quantile(mean_sat, probs = 0.025), 3),
    UCL = round(quantile(mean_sat, probs = 0.975), 3)) %>% 
  mutate(ecoregion = factor(WSA9)) %>%
  #mutate(type = "MR") %>%
  select(ecoregion, estimate, LCL, UCL) %>%
  mutate(ecoregion = fct_reorder(ecoregion, estimate)) %>%
  ggplot( aes( x = ecoregion, y = estimate ) ) +
  geom_point() +
  geom_linerange( aes( ymin = LCL, ymax = UCL)) +
  geom_hline(yintercept = 1, color='blue') +
  ylab("mean N2O saturation ratio") +
  coord_flip() + 
  theme_bw() +
  ggtitle("Mean (+/- 95% CI) predicted N2O saturation ratio")

# density plots of predicted distribution
# huge right tail
p <- all_predictions %>%
  #filter(.draw %in% 1:10) %>% # subset for practice
  mutate(ecoregion = factor(WSA9)) %>%
  mutate(ecoregion = fct_reorder(ecoregion, n2osat)) %>%
  ggplot( aes( x = n2osat, group = .draw, color = .draw ) ) +
  geom_density(show.legend = FALSE) +
  geom_vline(xintercept = 1, color = "red") +
  xlab("N2O saturation ratio") +
  xlim(0,5) + # data range is 0-300, but sample max is 30
  facet_wrap(~ecoregion) +
  theme_bw()
